---
title: "GxE Finlay-Wilkinson Analysis Report"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y - %H:%M:%S')`"
params: 
    colorby: null
    trait: null
    data: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(statgenGxE)
```
```{r, echo=FALSE}
htmltools::img(src = "sticker.png", 
               alt = 'logo',
               width = '150px',
               style = 'position:absolute; top:0; left:0; padding:10px;')
```

## Studies:
```{r}
knitr::kable(unique(rv_gxe$data[,.(trialName, locationName, studyDbId, studyName)])[studyDbId%in%input$picker_env])
```

## Trait: `r params$trait`
## Analysis output
```{r, echo=FALSE}
summary(rv_gxe$TDFW)
```

## FW plot

### Main plot
```{r, fig.height=10, fig.width=10, eval=TRUE, message=FALSE, warning=FALSE, results='hide'}
        TDFWplot <- rv_gxe$TDFWplot
        if (any(colnames(rbindlist(rv$TD))=="scenario")){
          ts <- rbindlist(rv$TD)[,.N,.(trial, scenario)]
          ts [,newtrial:=paste0(trial," (",scenario,")")]
          TDFWplot$fittedGeno$trial <- ts$newtrial[match(TDFWplot$fittedGeno$trial, ts$trial)]
          TDFWplot$envEffs$Trial <- ts$newtrial[match(TDFWplot$envEffs$Trial, ts$trial)]
          TDFWplot$TD <- rename_envs(TDFWplot$TD, ts$trial, ts$newtrial)
        }
        if (is.null(input$FW_picker_color_by) || input$FW_picker_color_by=="sensitivity clusters"  || input$FW_picker_color_by=="Nothing"){
            p <- plot(TDFWplot, plotType = "line", output = F)
        } else {
            if (!input$FW_picker_color_by%in%colnames(TDFWplot$TD)){
                TDFWplot$TD <- lapply(seq_along(TDFWplot$TD),function(a) data.table(TDFWplot$TD[[a]])[data.table(rv$TD[[a]])[,.SD, .SDcols=c("genotype",input$FW_picker_color_by)], on=.(genotype)])
            }

           p <- plot(TDFWplot, plotType = "line", colorGenoBy=input$FW_picker_color_by,output = F)
           # In case there is only two classes in color geno by
           # rebuild the line plot so that the smallest class is on top
           if (length(unique(p$data[[input$FW_picker_color_by]]))==2){
             levs <- names(sort(table(p$data[[input$FW_picker_color_by]])))
             cols <- getOption("statgen.genoColors")[1:2]
             names(cols) <- levs
             # Remove existing geom_point and geom_line layers
             p$layers[[1]] <- NULL
             p$layers[[2]] <- NULL
             p <- p + 
               ggplot2::geom_line(data=p$data[p$data[[input$FW_picker_color_by]]==levs[2],], aes(y = fitted, color=get(input$FW_picker_color_by)), size=0.5) +
               ggplot2::geom_point(data=p$data[p$data[[input$FW_picker_color_by]]==levs[2],], aes(y = fitted, color=get(input$FW_picker_color_by)), size=1) +
               ggplot2::geom_line(data=p$data[p$data[[input$FW_picker_color_by]]==levs[1],], aes(y = fitted, color=get(input$FW_picker_color_by)), size=2) +
               ggplot2::geom_point(data=p$data[p$data[[input$FW_picker_color_by]]==levs[1],], aes(y = fitted, color=get(input$FW_picker_color_by)), size=2) +
               scale_color_manual(values=cols)
           }

    }
     p <- p + theme(legend.title = element_text(angle = 90))
     
     if (!input$FW_coord_equal){
       p + coord_cartesian()
     } else {
      p
    }

    
```
<!-- Optional Sensitivity Clusters section -->

```{asis, echo = "sensitivity_cluster"%in%colnames(rbindlist(TDFWplot$TD))}
### Sensitivity Clusters
Genotypes were clustered based on Finlay Wilkinson results using the following parameters :
```

`r if ("sensitivity_cluster"%in%colnames(rbindlist(TDFWplot$TD))){paste0("- Number of clusters: ", input$FW_cluster_sensitivity_nb )}`

`r if ("sensitivity_cluster"%in%colnames(rbindlist(TDFWplot$TD))){paste0("- Clustering on: ", paste(input$FW_picker_cluster_on, collapse=", "))}`

`r if ("sensitivity_cluster"%in%colnames(rbindlist(TDFWplot$TD))){paste0("- Clustering method: ", input$FW_picker_cluster_meth)}`


```{r, fig.height=10, fig.width=10, eval="sensitivity_cluster"%in%colnames(rbindlist(TDFWplot$TD)), message=FALSE, warning=FALSE, results='hide'}
          if("sensitivity_cluster"%in%colnames(rbindlist(TDFWplot$TD))){
            p <- plot(TDFWplot, plotType = "line", colorGenoBy="sensitivity_cluster", output=FALSE)
            print(p)
          
for (cl in sort(unique(rv_gxe$sensclust$sensitivity_cluster))){
              stacolors <- getOption("statgen.genoColors")
              names(stacolors)<-1:length(stacolors)
              p <- p + scale_color_grey(start = 0.8, end = 0.8, guide = "none") + ggtitle(label = paste0("Sensitivity cluster ",cl)) +
                ggnewscale::new_scale_color() + 
                ggplot2::geom_line(data=p$data[p$data$genotype%in%rv_gxe$sensclust[sensitivity_cluster==cl, Genotype],], aes(y = fitted, color=sensitivity_cluster), size=1) + scale_color_manual(values = stacolors)
              print(p)
}
}
```

<!-- Optional Selected genotypes section -->
### `r if (!is.null(input$FW_sens_clusters_DT_rows_selected)){"Selected genotypes"}`
`r if (!is.null(input$FW_sens_clusters_DT_rows_selected)){"Selected genotypes are :"}`

```{r, eval=!is.null(input$FW_sens_clusters_DT_rows_selected), warning=FALSE,  message=FALSE}
dtsc <- dcast(rbindlist(rv$TD)[,c("genotype","trial",input$picker_trait), with = F],genotype~trial)[rv_gxe$sensclust, on=.(genotype=Genotype)][,-c("SE_GenMean","SE_Sens","MSdeviation")]
genot_trial_counts <- rbindlist(rv$TD)[,.N,genotype]
dtsc <- genot_trial_counts[dtsc,on=.(genotype)]
knitr::kable(dtsc[input$FW_sens_clusters_DT_rows_selected,])
```

```{r, eval=!is.null(input$FW_sens_clusters_DT_rows_selected), fig.height=10, fig.width=10, message=FALSE, warning=FALSE, results='hide'}
              if (!is.null(input$FW_sens_clusters_DT_rows_selected)){
                #browser()
                rv_gxe$selected_genotypes <- rv_gxe$sensclust[input$FW_sens_clusters_DT_rows_selected,]$Genotype
                p <- plot(TDFWplot, plotType = "line", output = F)
                p <- p + scale_color_grey(start = 0.8, end = 0.8, guide = "none") +
                    ggnewscale::new_scale_color() + 
                    ggplot2::geom_line(data=p$data[p$data$genotype%in%rv_gxe$selected_genotypes,], aes(y = fitted, color=genotype), size=2) + 
                    geom_point(data=p$data[p$data$genotype%in%rv_gxe$selected_genotypes,], aes(color=genotype), size=3) + theme(legend.position = "right")
                    #if (input$FW_display_raw_data){
                    #  p <- p + geom_point(data=as.data.table(p$data)[rbindlist(rv$TD)[genotype%in%rv_gxe$selected_genotypes,c("genotype", "trial" ,input$picker_trait), with=FALSE], on=.(genotype, trial)], aes(y=get(input$picker_trait), x=EnvMean, color=genotype), size=4, shape=1, stroke=2)
                    #}
                print(p + theme(legend.position = "bottom"))
              }
```

#### `r if (!is.null(input$FW_sens_clusters_DT_rows_selected)){"Selected genotypes: trellis plot"}`
```{r, eval=TRUE,  message=FALSE, warning=FALSE, results='hide'}
 if (!is.null(input$FW_sens_clusters_DT_rows_selected)){
   trellis.fig.height=1+3*wrap_dims(length(input$FW_sens_clusters_DT_rows_selected))[1]
 } else {
   trellis.fig.height=10
 }
```

```{r, eval=!is.null(input$FW_sens_clusters_DT_rows_selected), fig.height=trellis.fig.height, fig.width=10, fig.width=10, message=FALSE, warning=FALSE, results='hide'}
                rv$selected_genotypes <- rv_gxe$sensclust[input$FW_sens_clusters_DT_rows_selected,]$Genotype
                p <- plot(TDFWplot, plotType = "trellis", genotypes=rv_gxe$selected_genotypes, output=FALSE)
                print(p)
```

